Automating Verification of MPC Security

### 2023-06-15 popl24/minicat.tex
checkpoint

\emph{Memories} are fundamental to the semantics of $\fedcat$ and
provide the random tape and secret inputs to protocols, and record
view assignments. Memories $\store$ are finite (partial) mapping from
variables to binary values $\beta \in \{0,1\}$. The \emph{domain} of a
memory is written $\dom(\store)$ and is the finite set of variables on
which the memory is defined. We write $\store\{ x \mapsto \beta\}$ for
$x\not\in\dom(\store)$ to denote the memory $\store'$ such that
$\store'(x) = \beta$ and otherwise $\store'(y) = \store(y)$ for all $y \in
\dom(\store)$.

Given a set of variables $X$, we write $\store_X$ to denoted the
memory $\store$ restricted to the domain $X$, and and we define
$\mems(X)$ as the set of all memories with domain $X$:
$$
\mems(X) \defeq \{ \store \mid \dom(\store) = X \}
$$
Thus, given a protocol $\prog$, the set of all random tapes for
$\prog$ is $\mems(\flips(\prog))$. We let $\stores$ range
over sets of memories with the same domain, and abusing notation
we write $\dom(\stores)$ to denote the common domain.

>>>>

\emph{Memories} are fundamental to the semantics of $\fedcat$ and
provide the random tape and secret inputs to protocols, and record
view assignments. Memories $\store$ are finite (partial) mapping from
variables to binary values $\beta \in \{0,1\}$. The \emph{domain} of a
memory is written $\dom(\store)$ and is the finite set of variables on
which the memory is defined. We write $\store\{ x \mapsto \beta\}$ for
$x\not\in\dom(\store)$ to denote the memory $\store'$ such that
$\store'(x) = \beta$ and otherwise $\store'(y) = \store(y)$ for all $y
\in \dom(\store)$. We write $\store_1 \subseteq \store_2$ iff
$\dom(\store_1) \subseteq \dom(\store_2)$ and $\store_1(x) =
\store_2(x)$ for all $x \in \dom(\store_1)$. We write $\store_1 \cap
\store_2$ to denote the combination of $\store_1$ and $\store_2$
assuming $\store_1(x) = \store_2(x)$ for all $x \in \dom(\store_1)
\cap \dom(\store_2)$, otherwise $\store_1 \cap \store_2$ is undefined.

Given a set of variables $X$, we write $\store_X$ to denoted the
memory $\store$ restricted to the domain $X$, and and we define
$\mems(X)$ as the set of all memories with domain $X$:
$$
\mems(X) \defeq \{ \store \mid \dom(\store) = X \}
$$
Thus, given a protocol $\prog$, the set of all random tapes for
$\prog$ is $\mems(\flips(\prog))$. We let $\stores$ range
over sets of memories with the same domain, and abusing notation
we write $\dom(\stores)$ to denote the common domain,
and $\stores_X = \{ \store_X | \store \in \stores \}$.

### 2023-06-15 popl24/pmf.tex
checkpoint

\subsection{Basic Definitions} We begin by defining memory probability distributions as follows.
\begin{definition}
  A \emph{memory probability distribution} $\pdf{X}$ is a function
  mapping memories in $\mems(X)$ to values in $[0..1]$, such that:
  $$
  \sum_{\store \in \mems(X)} \pdf{X}(\store) \  = \ 1
  $$
  We call $X$ the \emph{domain} of $\pdf{X}$.
\end{definition}
To recover succinct and familiar notation, we may omit the domain of a
distribution when it is clear from an application context-
i.e., we allow the following sugaring:
$$
\pdf{}(\store) \defeq \pdf{\dom(\store)}(\store)
$$
Now, we can define a notion of marginal and conditional
distributions as follows, which are standard for discrete
probability mass functions. 
\begin{definition}
  Given $X$ the \emph{marginal distribution} of $Y \subseteq X$
  in a distribution $\pdf{X}$, denoted $\margd{\pdf{X}}{Y}$,
  is a distribution with domain $Y$ where for all
  $\store \in \mems(Y)$:
  $$
  (\margd{\pdf{X}}{Y})(\store) =
  \sum_{\store' \in \mems(X-Y)} \pdf{X}(\store \cup \store')
  $$
\end{definition}

\begin{definition}
  Given $\pdf{X}$, its \emph{conditional distribution given
  $\store$} with $\dom(\store) = Y$ and $Y \subseteq X$, denoted
  $\condd{\pdf{X}}{\store}$, is a distribution with domain $X - Y$ where for all
  $\store' \in \mems(X - Y)$:
  $$
  (\condd{\pdf{X}}{\store})(\store') =
      \pdf{X}(\store \cup \store') / ((\margd{\pdf{X}}{Y})(\store))
  $$
\end{definition}
To recover familiar notation we allow the following syntactic
sugarings:
\begin{eqnarray*}
\pdf{X}(\store|\store') &\defeq& (\condd{\pdf{X}}{\store})(\store')\\
\pdf{X}(\store) &\defeq& (\margd{\pdf{X}}{\dom(\store)})(\store) \qquad \dom(\store) \subset X
\end{eqnarray*}

@@

\subsection{Examples}

>>>>

\subsection{Basic Definitions} We begin by defining memory probability distributions as follows.
\begin{definition}
  A \emph{memory probability distribution} $\pdf{X}$ is a function
  mapping memories in $\mems(X)$ to values in $[0..1]$, such that:
  $$
  \sum_{\store \in \mems(X)} \pdf{X}(\store) \  = \ 1
  $$
  We call $X$ the \emph{domain} of $\pdf{X}$.
\end{definition}
To recover succinct and familiar notation, we may omit the domain of a
distribution when it is clear from an application context-
i.e., we allow the following sugaring:
$$
\pdf{}(\store) \defeq \pdf{\dom(\store)}(\store)
$$
Now, we can define a notion of marginal and conditional
distributions as follows, which are standard for discrete
probability mass functions. 
\begin{definition}
  Given $X$ the \emph{marginal distribution} of $Y \subseteq X$
  in a distribution $\pdf{X}$, denoted $\margd{\pdf{X}}{Y}$,
  is a distribution with domain $Y$ where for all
  $\store \in \mems(Y)$:
  $$
  (\margd{\pdf{X}}{Y})(\store) =
  \sum_{\store' \in \mems(X-Y)} \pdf{X}(\store \cap \store')
  $$
\end{definition}

\begin{definition}
  Given $\pdf{X}$, its \emph{conditional distribution given
  $\stores$} with $\dom(\stores) = Y$ and $Y \subseteq X$, denoted
  $\condd{\pdf{X}}{\stores}$, is a distribution with domain $X$ where for all
  $\store \in \mems(X)$:
  $$
  (\condd{\pdf{X}}{\stores})(\store) =
  (\sum_{\store' \in \stores} \pdf{X}(\store \cap \store')) /
  (\sum_{\store' \in \stores} \pdf{X}(\store'))
  $$
  where $\pdf{X}(\store \cap \store')) = 0$ if $\store \cap \store'$ is undefined.
  we write $\condd{\pdf{X}}{\store}$ as an abbreviation for $\condd{\pdf{X}}{\{ \store \}}$.
\end{definition}
To recover familiar notation we allow the following syntactic
sugarings:
\begin{eqnarray*}
\pdf{X}(\store|\store') &\defeq& (\condd{\pdf{X}}{\store})(\store')\\
\pdf{X}(\store) &\defeq& (\margd{\pdf{X}}{\dom(\store)})(\store) \qquad \dom(\store) \subset X
\end{eqnarray*}

@@

\subsection{Examples}
\label{section-pmf-examples}
